Body size patterns

### 2019-07-25 MS_Analysis_3spp_4rivers_Patterns_from 2spp_bySpp.Rmd
update figures

vB <- 
  cd %>% mutate( age = year - cohort,
                 metaPop01 = ifelse(riverOrdered == 'wb obear', 0 ,1),
                 ydayCumul = yday + 365 * (year - cohort),
                 cf = observedWeight/observedLength^3 * 10000 ) %>%
    filter( ageInSamples %in% 1:9,
            age < 3, 
            year < 2016, area %in% c('inside','trib'), enc == 1
            #!(riverOrdered == 'wb mitchell' & ageInSamples > 8) #low sample sizes
            )

@@

vB <- left_join(vB, cohortStrength)

cohortStrengthWide <- spread(cohortStrength, species, cohortStrengthScaled) %>%
  rename(cohortStrengthScaledBKT = bkt,
         cohortStrengthScaledBNT = bnt,
         cohortStrengthScaledATS = ats
         ) %>%
  dplyr::select(-cohortStrength)

@@

vB$cohortStrengthScaledBKT <- ifelse(is.na(vB$cohortStrengthScaledBKT), -2.5, vB$cohortStrengthScaledBKT)
vB$cohortStrengthScaledBNT <- ifelse(is.na(vB$cohortStrengthScaledBNT), -2.5, vB$cohortStrengthScaledBNT)
vB$cohortStrengthScaledATS <- ifelse(is.na(vB$cohortStrengthScaledATS), -2.5, vB$cohortStrengthScaledATS)

ggplot(cohortStrength, aes(cohort, cohortStrengthScaled, group = species, linetype = species, shape = species, color = species)) +
  geom_point(size = 2) +
  geom_line(size = 1.1, color = 'grey40') +
  labs(x = 'Cohort',
       y = 'Cohort strength') +
  theme_publication() +
  facet_grid(~metaPop01)

@@

```{r dataIn}
dataIn <- vB %>% filter(cohort %in% 2000:2013, species %in% speciesIn)
```

@@

@@

# bkt
#   rowname       df      AIC
# 1    mod6 14.99337 429769.2
# 2    mod2 25.99569 432704.3
# 3    mod4 13.98558 433764.8

#bnt
#   rowname       df      AIC
# 1    mod6 12.99685 238636.2
# 2    mod2 17.99755 242840.1
# 3    mod4 11.98667 243594.3

@@

#using salmon01 * river because we need diff effects per river - even though AIC is worse for this model
modBKT <- bam(observedLength ~ riverFactor + factor(salmon01) +              
               s(ydayCumul, bs = 'cr') +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = riverFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortRiverFactor) +
               s(cohort, bs = 'cr', k = kIn, by = riverFactor) + 
               s(cohortStrengthScaled, bs = 'cr', k = kIn, by = riverFactor), 
             data = vB %>% filter(cohort %in% 2000:2013, species %in% 'bkt'), method = "REML")

predGridBKT <- expand.grid(riverFactor = unique(modBKT$model$riverFactor), 
                           cohortFactor = unique(modBKT$model$cohort),
                           ydayCumul = seq(250,1000, by = 14),
                           salmon01 = c(0,1),
                           cohortStrengthScaled = seq(-2.5,2.5, by = 0.25)) %>%
                    #left_join(., yDayAll) %>%
                    mutate(cohortRiverFactor = paste(cohortFactor, riverFactor, sep = '_'),
                           cohort = cohortFactor)

#################################
# Brown trout
# using CSr model becasue delta AIC is not huge btw it and CS3r. Better to have same models for both species
modBNT <- bam(observedLength ~ riverFactor + factor(salmon01) +              
               s(ydayCumul, bs = 'cr') +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = riverFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortRiverFactor) +
               s(cohort, bs = 'cr', k = kIn, by = riverFactor) + 
               s(cohortStrengthScaled, bs = 'cr', k = kIn, by = riverFactor), 
             data = vB %>% filter(cohort %in% 2000:2013, species %in% 'bnt'), method = "REML")

summary(modBNT)
#plot(modBNT,  scale = 0)

predGridBNT <- expand.grid(riverFactor = unique(modBNT$model$riverFactor), 
                           cohortFactor = unique(modBNT$model$cohort),
                           ydayCumul = seq(250,1000, by = 14),
                           salmon01 = c(0,1),
                           cohortStrengthScaled = seq(-2.5,2.5, by = 0.25)) %>%
                    #left_join(., yDayAll) %>%
                    mutate(cohortRiverFactor = paste(cohortFactor, riverFactor, sep = '_'),
                           cohort = cohortFactor)

# cohorts by river/species
ggplot(predGrid2Both %>% 
         filter(salmon01 ==0, cohortStrengthScaled == 0
#         (cohortStrengthScaledBKT == 0 & salmon01 == 0) | (cohortStrengthScaledBKT == 0 & cohortStrengthScaledBNT == 0 & cohortStrengthScaledATS == 0 & metaPop01 == 1 & salmon01 ==0)
           ),
#           cohortStrengthScaledBKT == 0, cohortStrengthScaledBNT == 0, cohortStrengthScaledATS == 0, metaPop01 == 1, salmon01 == 0),
       aes(ydayCumul, pred, group = cohort, color = cohort)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'Cohort') +
  scale_color_viridis_c(breaks = c(2000,2004,2008,2012), labels = c(2000,2004,2008,2012)) +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  guides(color = guide_colorbar(barheight = 10,
                                barwidth = 1.5,
                                ticks = FALSE,
                                nbin = 100)) +
#  guide_legend(title = 'Cohort') +
  facet_grid(speciesGG ~ riverGG, scales = 'free_y')

# specific spline effects by species
(plotCohort <- plotGamVarBySpecies(var = 's(cohort)', xAxisLab = 'Cohort'))
ggsave('./figures/cohortEffect.png', width = 11, height = 8, units='in')
(plotCohortStrength <- plotGamVarBySpecies(var = 's(cohortStrengthScaled)', xAxisLab = 'Cohort Strength'))
ggsave('./figures/cohortStrengthEffect.png', width = 11, height = 8, units='in')
#
plot.gam(modBKT, pages = 10)

# across rivers, by species
ggplot(predGrid2Both %>% 
         filter(salmon01 ==0, cohortStrengthScaled == 0, cohort == 2006, cohortStrengthScaled == 0),
       aes(ydayCumul, pred, group = speciesGG, color = speciesGG)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'Cohort') +
#  scale_color_viridis_c() +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  facet_wrap(~ riverGG)

# across species, by rivers
ggplot(predGrid2Both %>% 
         filter(salmon01 == 0, cohortStrengthScaled == 0, cohort == 2006, cohortStrengthScaled == 0),
       aes(ydayCumul, pred, group = riverGG, color = riverGG)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'River') +
  #scale_color_viridis_c() +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  facet_grid(~ speciesGG)

ggsave('./figures/ydayCumulAcrossSppByRiver.png', width = 11, height = 8, units='in')

# cohort effects

ggplot(tmp2, aes(x,y)) + geom_line()

>>>>

vB <- 
  cd %>% mutate( age = year - cohort,
                 metaPop01 = ifelse(riverOrdered == 'wb obear', 0 ,1),
                 ydayCumul = yday + 365 * (year - cohort),
                 cf = observedWeight/observedLength^3 * 10000 ) %>%
    filter( ageInSamples %in% 1:9,
            age < 3, 
            year < 2016, area %in% c('inside','trib'), enc == 1
            #!(riverOrdered == 'wb mitchell' & ageInSamples > 8) #low sample sizes
            ) %>%
    filter(!(cohort < 2002 & river %in% c('wb jimmy','wb mitchell','wb obear'))) # added 7/25/2019. Limits tribs to after 2002

@@

#ggplot(cohortStrength, aes(cohortStrengthScaled, color = species)) + geom_freqpoly()

vB <- left_join(vB, cohortStrength)
# 
# cohortStrengthWide <- spread(cohortStrength, species, cohortStrengthScaled) %>%
#   rename(cohortStrengthScaledBKT = bkt,
#          cohortStrengthScaledBNT = bnt,
#          cohortStrengthScaledATS = ats
#          ) %>%
#   dplyr::select(-cohortStrength) %>%
#   ungroup()

cohortStrengthWide <- cohortStrength %>%
  dplyr::select(-cohortStrength) %>%
  spread( species, cohortStrengthScaled) %>%
  rename(cohortStrengthScaledBKT = bkt,
         cohortStrengthScaledBNT = bnt,
         cohortStrengthScaledATS = ats
         ) %>%
  ungroup()

@@

vB$cohortStrengthScaledBKT2p5 <- ifelse(is.na(vB$cohortStrengthScaledBKT), -2.5, vB$cohortStrengthScaledBKT)
vB$cohortStrengthScaledBNT2p5 <- ifelse(is.na(vB$cohortStrengthScaledBNT), -2.5, vB$cohortStrengthScaledBNT)
vB$cohortStrengthScaledATS2p5 <- ifelse(is.na(vB$cohortStrengthScaledATS), -2.5, vB$cohortStrengthScaledATS)

vB$cohortStrength01BKT <- ifelse(is.na(vB$cohortStrengthScaledBKT), 0, 1)
vB$cohortStrength01BNT <- ifelse(is.na(vB$cohortStrengthScaledBNT), 0, 1)
vB$cohortStrength01ATS <- ifelse(is.na(vB$cohortStrengthScaledATS), 0, 1)

cohortStrength$speciesGG <- factor(cohortStrength$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"))

ggplot(cohortStrength %>% filter(cohort > 1999), aes(cohort, cohortStrengthScaled, group = speciesGG, shape = speciesGG, color = speciesGG)) +
  geom_point(size = 2) +
  geom_line(size = 1.2) +
  labs(x = 'Cohort',
       y = 'Cohort strength',
       shape = 'Species', color='Species') +
  theme_publication() +
 # scale_fill_grey() +
  theme(legend.position = "right", 
    legend.direction = "vertical",
    legend.title = element_text(face = "plain")) +
  facet_grid(metaPop01 ~ .)

ggsave('./figures/cohortStrengthByMetapop.png', width = 11, height = 8, units='in')

@@

```{r dataIn}
dataIn <- vB %>% filter(cohort %in% 2000:2013, species %in% speciesIn) %>%
  filter(!(cohort < 2002 & riverFactor %in% c('wb jimmy','wb mitchell','wb obear')))
```

@@

# bkt
#   rowname       df      AIC
# 1    mod6 14.82321 197082.8
# 2    mod2 25.99790 197663.0
# 3    mod4 13.96042 198350.4

#bnt
#   rowname       df       AIC
# 1    mod6 12.29048  98814.72
# 2    mod2 17.99609  99877.98
# 3    mod4 11.96329 100212.22

```{r remove cohort, focus on spp-specific cohort strengths}
#sppoke with keith. decided focus on cohrot is less interesting than river effects and density effects

mod1 <- bam(observedLength ~ riverFactor + factor(salmon01) +              
               s(ydayCumul, bs = 'cr') +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = riverFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortRiverFactor) +
               s(cohort, bs = 'cr', k = kIn, by = riverFactor) +
               s(cohortStrengthScaledBKT, bs = 'cr', k = kIn, by = riverFactor) +
               s(cohortStrengthScaledBNT2p5, bs = 'cr', k = kIn, by = riverFactor), 
  #             s(cohortStrengthScaledATS2p5, bs = 'cr', k = kIn),
             data = dataIn, method = "REML")
summary(modCS3)
#plot(modCS3, pages = 8)

mod2 <- bam(observedLength ~ riverFactor + factor(salmon01) +              
               s(ydayCumul, bs = 'cr') +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = riverFactor) +
               #s(ydayCumul, bs = 'cr', k = kIn, by = cohortRiverFactor) +
               s(cohort, bs = 'cr', k = kIn, by = riverFactor) +
               s(cohortStrengthScaledBKT, bs = 'cr', k = kIn, by = riverFactor) +
               s(cohortStrengthScaledBNT2p5, bs = 'cr', k = kIn, by = riverFactor), 
  #             s(cohortStrengthScaledATS2p5, bs = 'cr', k = kIn),
             data = dataIn, method = "REML")

mod3 <- bam(observedLength ~ riverFactor + factor(salmon01) +              
               s(ydayCumul, bs = 'cr') +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = riverFactor) +
               #s(ydayCumul, bs = 'cr', k = kIn, by = cohortRiverFactor) +
               s(cohort, bs = 'cr', k = kIn, by = riverFactor) +
               s(cohortStrengthScaledBKT, bs = 'cr', k = kIn, by = riverFactor),
              # s(cohortStrengthScaledBNT2p5, bs = 'cr', k = kIn, by = riverFactor), 
  #             s(cohortStrengthScaledATS2p5, bs = 'cr', k = kIn),
             data = dataIn, method = "REML")

mod4 <- bam(observedLength ~ riverFactor + factor(salmon01) +              
               s(ydayCumul, bs = 'cr') +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = riverFactor) +
               #s(ydayCumul, bs = 'cr', k = kIn, by = cohortRiverFactor) +
               s(cohort, bs = 'cr', k = kIn, by = riverFactor),
              # s(cohortStrengthScaledBKT, bs = 'cr', k = kIn, by = riverFactor) +
              # s(cohortStrengthScaledBNT2p5, bs = 'cr', k = kIn, by = riverFactor), 
  #             s(cohortStrengthScaledATS2p5, bs = 'cr', k = kIn),
             data = dataIn, method = "REML")

AIC(mod1,mod2,mod3,mod4) %>% rownames_to_column() %>% arrange(AIC)
```

modBKT <- bam(observedLength ~ riverFactor + factor(salmon01) +              
               s(ydayCumul, bs = 'cr') +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = riverFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortRiverFactor) +
               s(cohort, bs = 'cr', k = kIn, by = riverFactor) +
               s(cohortStrengthScaledBKT, bs = 'cr', k = kIn, by = riverFactor) +
               s(cohortStrengthScaledBNT2p5, bs = 'cr', k = kIn, by = riverFactor),

             data = vB %>% filter(cohort %in% 2000:2013, species %in% 'bkt'), method = "REML")

predGridBKT <- expand.grid(riverFactor = unique(modBKT$model$riverFactor), 
                           cohortFactor = unique(modBKT$model$cohort),
                           ydayCumul = seq(250,1000, by = 14),
                           salmon01 = c(0,1),
                           cohortStrengthScaledBKT = seq(-2.5,2.5, by = 0.25),
                           cohortStrengthScaledBNT2p5 = seq(-2.5,2.5, by = 0.25)) %>%
                    #left_join(., yDayAll) %>%
                    mutate(cohortRiverFactor = paste(cohortFactor, riverFactor, sep = '_'),
                           cohort = cohortFactor) %>%
                    filter(!(cohort < 2002 & riverFactor %in% c('wb jimmy','wb mitchell','wb obear')))

#################################
# Brown trout
# using CSr model becasue delta AIC is not huge btw it and CS3r. Better to have same models for both species

modBNT <- bam(observedLength ~ riverFactor + factor(salmon01) +              
               s(ydayCumul, bs = 'cr') +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = riverFactor) +
               s(ydayCumul, bs = 'cr', k = kIn, by = cohortRiverFactor) +
               s(cohort, bs = 'cr', k = kIn, by = riverFactor) +
               s(cohortStrengthScaledBKT, bs = 'cr', k = kIn, by = riverFactor) +
               s(cohortStrengthScaledBNT2p5, bs = 'cr', k = kIn, by = riverFactor),

             data = vB %>% filter(cohort %in% 2000:2013, species %in% 'bnt'), method = "REML")

summary(modBNT)
#plot(modBNT,  pages = 8,scale = 0)

predGridBNT <- expand.grid(riverFactor = unique(modBNT$model$riverFactor), 
                           cohortFactor = unique(modBNT$model$cohort),
                           ydayCumul = seq(250,1000, by = 14),
                           salmon01 = c(0,1),
                           cohortStrengthScaledBKT = seq(-2.5,2.5, by = 0.25),
                           cohortStrengthScaledBNT2p5 = seq(-2.5,2.5, by = 0.25)) %>%
                    #left_join(., yDayAll) %>%
                    mutate(cohortRiverFactor = paste(cohortFactor, riverFactor, sep = '_'),
                           cohort = cohortFactor) %>%
                    filter(!(cohort < 2002 & riverFactor %in% c('wb jimmy','wb mitchell','wb obear')))

predGrid2Both <- predGrid2Both %>% filter(!(cohort < 2002 & riverFactor %in% c('wb jimmy','wb mitchell','wb obear')))

# cohorts by river/species
ggplot(predGrid2Both %>% 
         filter(salmon01 ==0, cohortStrengthScaledBKT == 0, cohortStrengthScaledBNT2p5 == 0
#         (cohortStrengthScaledBKT == 0 & salmon01 == 0) | (cohortStrengthScaledBKT == 0 & cohortStrengthScaledBNT == 0 & cohortStrengthScaledATS == 0 & metaPop01 == 1 & salmon01 ==0)
           ),
#           cohortStrengthScaledBKT == 0, cohortStrengthScaledBNT == 0, cohortStrengthScaledATS == 0, metaPop01 == 1, salmon01 == 0),
       aes(ydayCumul, pred, group = cohort, color = cohort)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'Cohort') +
  scale_color_viridis_c(breaks = c(2000,2004,2008,2012), labels = c(2000,2004,2008,2012)) +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  guides(color = guide_colorbar(barheight = 10,
                                barwidth = 1.5,
                                ticks = FALSE,
                                nbin = 100)) +
#  guide_legend(title = 'Cohort') +
  facet_grid(speciesGG ~ riverGG, scales = 'free_y')

# specific spline effects by species
(plotCohort <- plotGamVarBySpecies(var = 's(cohort)', xAxisLab = 'Cohort'))
ggsave('./figures/cohortEffect.png', width = 11, height = 8, units='in')

(plotCohortStrength <- plotGamVarBySpecies(var = 's(cohortStrengthScaledBKT)', xAxisLab = 'Brook Trout cohort Strength'))
ggsave('./figures/cohortStrengthEffectBKT.png', width = 11, height = 8, units='in')

(plotCohortStrengthScaledBNT2p5 <- plotGamVarBySpecies(var = 's(cohortStrengthScaledBNT2p5)', xAxisLab = 'Brown Trout cohort Strength'))
ggsave('./figures/cohortStrengthEffectBNT.png', width = 11, height = 8, units='in')

#
#plot.gam(modBKT, pages = 10)

# across rivers, by species
ggplot(predGrid2Both %>% 
         filter(salmon01 == 0, cohortStrengthScaledBKT == 0, cohort == 2006, cohortStrengthScaledBNT2p5 == 0),
       aes(ydayCumul, pred, group = speciesGG, color = speciesGG)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'Cohort') +
#  scale_color_viridis_c() +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  facet_wrap(~ riverGG)

# across species, by rivers
ggplot(predGrid2Both %>% 
         filter(salmon01 == 0, cohortStrengthScaledBKT == 0, cohort == 2006, cohortStrengthScaledBNT2p5 == 0),
       aes(ydayCumul, pred, group = riverGG, color = riverGG)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'River') +
  #scale_color_viridis_c() +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  facet_grid(rows = vars(speciesGG))

ggsave('./figures/ydayCumulAcrossSppByRiver.png', width = 8, height = 8, units='in')

# river effects 
# BKT
plotBKTAll <- plot.gam(modBKT, page = 9)
plotBKTAll[[16]]$ylab # WB

plotBKTByRiver <- data.frame()
bktRiver1 <- 16
for(i in 1:4){
  ii <- i + bktRiver1 - 1
  tmp <- data.frame(x = plotBKTAll[[ii]]$x, y = plotBKTAll[[ii]]$fit, se = plotBKTAll[[i]]$se, ylab = plotBKTAll[[ii]]$ylab, riverIndex = i) %>% mutate(species = 'bkt', upperCI = y + se * 1.96, lowerCI = y - se * 1.96)
  plotBKTByRiver <- rbind(plotBKTByRiver, tmp)
}

#BNT
plotBNTAll <- plot.gam(modBNT, page = 6)
plotBNTAll[[16]]$ylab # WB

plotBNTByRiver <- data.frame()
bntRiver1 <- 16
for(i in 1:2){
  ii <- i + bntRiver1 - 1
  tmp <- data.frame(x = plotBNTAll[[ii]]$x, y = plotBNTAll[[ii]]$fit, se = plotBNTAll[[i]]$se, ylab = plotBNTAll[[ii]]$ylab, riverIndex = i) %>% mutate(species = 'bnt', upperCI = y + se * 1.96, lowerCI = y - se * 1.96)
  plotBNTByRiver <- rbind(plotBNTByRiver, tmp)
}

plotByRiver <- rbind(plotBKTByRiver, plotBNTByRiver)

plotByRiver$speciesGG <- factor(plotByRiver$species, levels = c('bkt','bnt','ats'), labels = c("Brook Trout", "Brown Trout", "Atlantic Salmon"), ordered = T)
plotByRiver$riverGG <- factor(plotByRiver$riverIndex,
                         levels=c(1,2,3,4),
                         labels = c("West Brook","Open Large","Open Small","Isolated Small"))

ggplot(plotByRiver, aes(x)) +
  geom_line(aes(y = y, color = speciesGG), size = 1.5) +
  geom_ribbon(aes(ymin = lowerCI, ymax = upperCI, fill = speciesGG), alpha = 0.5, show.legend = FALSE) +
  scale_color_manual(values = c('grey30', 'grey70')) +
  scale_fill_manual(values = c('grey30', 'grey70')) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'Species') +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face="plain")) +
  facet_wrap(~ riverGG)

ggsave('./figures/ydayCumulAcrossRiversBySpecies.png', width = 11, height = 8, units='in')

@@

@@
